Posterior summarisation in Bayesian phylogenetics using Tracer 1.7

### 2018-01-31 manuscript/tracer17.tex
revert to original author-order

\author[Rambaut \textit{et~al.}]{
Andrew Rambaut\,$^{1}$,
Guy Baele$^{2}$,
Dong Xie\,$^{3,4}$,
Alexei J.~Drummond\,$^{3,4}$,
Marc A.~Suchard\,$^{5,6}$
}

\address{
$^{1}$Institute of Evolutionary Biology, University of Edinburgh, Edinburgh, UK\\
$^{2}$Department of Microbiology and Immunology, Rega Institute, KU Leuven, Leuven, Belgium\\
$^{3}$Department of Computer Science, University of Auckland, Auckland, NZ\\
$^{4}$Centre for Computational Evolution, University of Auckland, Auckland, NZ\\
$^{5}$Department of Human Genetics, University of California, Los Angeles, USA \\
$^{6}$Department of Biostatistics, University of California, Los Angeles, USA \\
%$^{7}$Department of Human Genetics, David Geffen School of Medicine at UCLA, University of California, Los Angeles, USA\\
}

>>>>

\author[Rambaut \textit{et~al.}]{
Andrew Rambaut\,$^{1}$,
Alexei J.~Drummond\,$^{2,3}$,
Guy Baele$^{4}$,
Dong Xie\,$^{2,3}$,
Marc A.~Suchard\,$^{5,6}$
}

\address{
$^{1}$Institute of Evolutionary Biology, University of Edinburgh, Edinburgh, UK \\
$^{2}$Department of Computer Science, University of Auckland, Auckland, NZ \\
$^{3}$Centre for Computational Evolution, University of Auckland, Auckland, NZ \\
$^{4}$Department of Microbiology and Immunology, Rega Institute, KU Leuven, Leuven, Belgium\\
$^{5}$Department of Human Genetics, University of California, Los Angeles, USA \\
$^{6}$Department of Biostatistics, University of California, Los Angeles, USA \\
%$^{7}$Department of Human Genetics, David Geffen School of Medicine at UCLA, University of California, Los Angeles, USA\\
}
